\begin{thebibliography}{9}
\bibitem{bib1}
A. Efros and T. K. Leung.  Texture synthesis by non-parametric sampling. In Computer Vision, 1999. The Proceedings of the Seventh IEEE International Conference on,volume 2, pages 1033–1038. IEEE, 1999.

\bibitem{bib2}
L. Wei and M. Levoy.  Fast texture synthesis using tree-structured vector quantization. In Proceedings of the 27th annual conference on Computer graphics and interactive techniques, pages 479–488. ACM Press/Addison-Wesley Publishing Co., 2000.

\bibitem{bib3}
A. A. Efros and W. T. Freeman.  Image quilting for texture synthesis and transfer. In Proceedings of the 28th annual conference on Computer graphics and interactive techniques, pages 341–346. ACM, 2001.

\bibitem{bib4}
V. Kwatra, A. Schodl, I. Essa, G. Turk, and A. Bobick. Graph cut textures: image and video synthesis using graph cuts. In ACM Transactions on Graphics (ToG), volume 22,pages 277–286. ACM, 2003.

\bibitem{bib5}
H. Lee, S. Seo, S. Ryoo, and K. Yoon. Directional Texture Transfer. In Proceedings of the 8th International Symposium on Non-Photo realistic Animation and Rendering, NPAR ’10,pages 43–48, New York, NY, USA, 2010. ACM.

\bibitem{bib6}
A. Krizhevsky, I. Sutskever, and G. E. Hinton.  Image net classification with deep convolutional neural networks. In Advances in neural information processing systems, pages1097–1105, 2012.

\bibitem{bib7}
J. Donahue, Y. Jia, O. Vinyals, J. Hoffman, N. Zhang,E. Tzeng, and T. Darrell.   DeCAF: A Deep Convolutional Activation Feature for Generic Visual Recognition.arXiv:1310.1531 [cs], Oct. 2013. arXiv: 1310.1531

\bibitem{bib8}
M. Cimpoi, S. Maji, and A. Vedaldi. Deep filter banks for texture recognition and segmentation. In Proceedings of the IEEE Conference on Computer Vision and Pattern Recognition, pages 3828–3836, 2015.

\bibitem{bib9}
S. Karayev, M. Trentacoste, H. Han, A. Agarwala, T. Darrell,A. Hertzmann, and H. Winnemoeller.  Recognizing imagestyle.arXiv preprint arXiv:1311.3715, 2013.

\bibitem{bib10}
Lin, T.Y., Maire, M., Belongie, S., Hays, J., Perona, P., Ramanan, D., Dollar, P.,Zitnick, C.L.:  Microsoft COCO: Common objects in context.  In: ECCV, 2014. 

\bibitem{bib11}
[11] Li, Y., Fang, C., Yang, J., Wang, Z., Lu, X., Yang, M.H.:  Universal style transfer via feature transforms.  In: NIPS, 2017. 

\bibitem{bib12}
[12] Reinhard, E., Ashikhmin, M., Gooch, B., Shirley, P.: Color transfer between images.IEEE Computer graphics and applications21(5) (2001) 34–41.

\bibitem{bib13}
[13] Freedman, D., Kisilev, P.:  Object-to-object color transfer: Optimal flows and smsp transformations.  In: CVPR, 2010. 

\bibitem{bib14}
[14] Shih,  Y.,  Paris,  S.,  Durand,  F.,  Freeman,  W.T.:   Data-driven  hallucination  of different times of day from a single outdoor photo.  In: SIGGRAPH, 2013.  

\bibitem{bib15}
[15] Li,  C.,  Wand,  M.:   Combining  markov  random  fields  and  convolutional  neural networks for image synthesis.  In: CVPR, 2016. 

\bibitem{bib16}
[16] Ulyanov, D., Lebedev, V., Vedaldi, A., Lempitsky, V.:  Texture networks: Feed-forward synthesis of textures and stylized images.  In: ICML, 2016.

\bibitem{bib17}
[17] Johnson, J., Alahi, A., Fei-Fei, L.:  Perceptual losses for real-time style transfer and super-resolution.  In: ECCV, 2016.

\bibitem{bib18}
Nikulin,  Y.,  Novak,  R.:  Exploring  the  neural  algorithm  of  artistic  style.  CoRRabs/1602.07188, 2016.

\bibitem{bib19}
X. Huang and S. Belongie. Arbitrary style transfer in real-time with adaptive instance normalization. In
ICCV, 2017.
\end{thebibliography}